---
title: "Assignment 1"
author: "lohith"
date: "2023-10-22"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(caret)
library(dplyr)
library(ISLR)
library(glmnet)
```


#loading and selecting required columns from ISLR carseats dataset
```{r}
carseats <- Carseats %>% select("Sales", "Price",
"Advertising","Population","Age","Income","Education")

```

#Scaling	of	the	the	carseats	dataset	using	preProcess	function	from	Caret	package
```{r}
carseats_scaled <- preProcess(carseats, method = c("scale", "center"))
carseats_predict<- predict(carseats_scaled, carseats)
summary(carseats_predict)
```

#Creating	a	matrix	for	glmnet	library	for	current	dataset.
```{r}
y <- carseats_predict$Sales
x<- data.matrix(carseats_predict[,c("Price",
"Advertising","Population","Age","Income","Education")])
```

#QB1.	Build	a	Lasso	regression	model	to	predict	Sales	based	on	all	other	attributes.
```{r}
lasso_model<- cv.glmnet(x, y, alpha = 1)
plot(lasso_model)
```


```{r}
best_lambda <- lasso_model$lambda.min
best_lambda
```
#The best value of lambda is 0.001524481 

#QB2.The	coefficient	for	the	price	(normalized)	attribute	in	the	best	model
```{r}
price_coef<- coef(lasso_model, s= "lambda.min")
price_coef

```
#The coefficient for the price is -4.793834e-01.

#QB3.Changing	Lambda	value	to	0.01	and	0.1
```{r}
lasso_model1<- cv.glmnet(x, y, alpha = 0.01)
best_lambda1 <- lasso_model1$lambda.min
best_lambda1
```
```{r}
coef<- coef(lasso_model1, s = "lambda.min")
coef
```
#Changing Lambda value to 0.1
```{r}
lasso_model2<- cv.glmnet(x, y, alpha = 0.1)
best_lambda2 <- lasso_model2$lambda.min
best_lambda2

coef1<- coef(lasso_model2, s = "lambda.min")
coef1
```
#The comparison between changing the lambda value shows that all the attributes remain in the model, even after changing the lambda.

#QB4.	Build	an	elastic-net	model	with	alpha	set	to	0.6.
```{r}
elastic_model<- cv.glmnet(x, y, alpha = 0.6)
best_lambda3<- elastic_model$lambda.min
best_lambda3

coef2<- coef(lasso_model2, s = "lambda.min")
coef2
```
#The best value of lambda for current model is 0.002315083